---
title: "Course Practical Machine Learning Peer Assessment"
author: "Oscar Vasquez,         Date: 12-Nov-2020"
output: html_document
---

The goal of this project is to predict the manner in which they did the exercise. 
This is the "classe" variable in the training set. 
I will use any of the other variables to predict with. 
I will create a report describing how you built your model, 
how I used cross validation, what I think the expected out of sample error 
is, and why I made the choices I did. 
I will also use your prediction model to predict 20 different test cases.  
This study is possible thank to  
http://web.archive.org/web/20161224072740/http:/groupware.les.inf.puc-rio.br/har
So thank you very much!  

```{r first, message=FALSE,warning=FALSE,cache=TRUE}  
#Libraries
library(AppliedPredictiveModeling)
library(caret)
library(corrplot)
library(dplyr)
library(e1071)
library(knitr)
library(ggplot2)
library(randomForest)
library(rpart)
setwd("D:/Trabajo/R/Curso8")
set.seed(2)
#Load Data
TrainUrl<-"https://d396qusza40orc.cloudfront.net/predmachlearn/pml-training.csv"
TestUrl<- "https://d396qusza40orc.cloudfront.net/predmachlearn/pml-testing.csv"
TrainFile <- "./Data/pml-training.csv"
TestFile  <- "./Data/pml-testing.csv"
if (!file.exists("./Data")) {
  dir.create("./Data")}
if (!file.exists(TrainFile)) {
  download.file(TrainUrl, destfile=TrainFile)}
if (!file.exists(TestFile)) {
  download.file(TestUrl, destfile=TestFile)}
Train <- read.csv("./Data/pml-training.csv",header=T,sep=",",
                     na.strings=c("NA",""))
Test <- read.csv("./Data/pml-testing.csv",header=T,sep=",",
                    na.strings=c("NA",""))
dim(Train)
dim(Test)
```

Files have 160 variables so its large to see data structure, so I will see just one data structure, lets say Train, Test should be the same structure.

```{r second, message=FALSE,warning=FALSE,cache=TRUE}
str(Train)
```

Now I will clean data, for ramdom forest I will select record with more than 60% of data and Variable "X" has a N row indicator so we should not use it to predict classes.

```{r Third, message=FALSE,warning=FALSE,cache=TRUE}
Train_clean <-Train[,-1]
Test_clean <-Test[,-1]
goodColumns <- c((colSums(!is.na(Train_clean[,-ncol(Train_clean)])) >= 0.6*nrow(Train_clean)))
Train_clean <-Train_clean[,goodColumns]
Test_clean <-Test_clean[,goodColumns]
dim(Train)
dim(Train_clean)
dim(Test)
dim(Test_clean)
```

Lets select training and test for modeling, 80/20.

```{r Fourth, message=FALSE,warning=FALSE,cache=TRUE}
TestIndex = createDataPartition(Train_clean$classe, p=0.80, list=F)
Training = Train_clean[TestIndex,]
Testing = Train_clean[-TestIndex,]
dim(Training)
dim(Testing)
```

Lest Run a Random Forest

```{r Six, message=FALSE,warning=FALSE,cache=TRUE}
RF1 <- randomForest(classe~.,data=Training)
RF1
importance(RF1)
```

It seems pretty good, really high acuraccy, let clasify Test, for this a trick, predict command will not work with a difference in data types, here we can use R coersity . I will add one case from Training, in order to give same types to all our variables in Test_clean, and when I call predict I will exclude this record

```{r Seven, message=FALSE,warning=FALSE,cache=TRUE}

Test_clean <- rbind(Training[100,1:58], Test_clean[1:58])

Pred_RF1 <- predict(RF1,newdata=Test_clean[-1,])

Pred_RF1
```

Now a little piece of code to create files with outcomes, remember Knit has its own Knit directory, so set it properly

```{r Eigth, message=FALSE,warning=FALSE,cache=TRUE}
for(i in 1:20){
    filename = paste0("./Data/Answer/Output_id_",i,".txt")
    write.table(Pred_RF1[i],file=filename,quote=FALSE,row.names=FALSE,col.names=FALSE)
  }

```

















